Precise temporal localisation of M/EEG effects with Bayesian generalised additive multilevel models

### 2025-02-14 brms_meeg.tex
pushin new simulation results and updated title and abstract

\title{Modelling M/EEG data with Bayesian generalised additive
multilevel models}

\shorttitle{Bayesian M/EEG modelling}

@@

\abstract{Time-resolved electrophysiological measurements such as those
offered by magneto- or electro-encephalography (M/EEG) provide a unique
window onto neural activity underlying cognitive process and how they
unfold over time. Typically, we are interested in testing whether such
measures differ across conditions and/or groups. The conventional
approach consists in conducting mass-univariate statistics through
followed by some form of multiplicity correction (e.g., FDR, FWER) or
cluster-based inference. However, these cluster-based methods have an
important downside: they shift the focus of inference from the timepoint
to the cluster level, thus preventing any conclusion to be made about
the onset and offset of effects (e.g., differences across conditions).
Here, we introduce a novel \emph{model-based approch} for analysing
one-dimensional M/EEG timeseries such as ERPs or decoding timecourses
and their differences across conditions or group. This approach relies
on Bayesian generalised additive multilevel models, which output the
posterior probabilility of the effect being above 0 (or above chance) at
every timestep, while naturally taking into account the temporal
dependencies and between-subject variability present in such data.}

@@

\hypertarget{toc}{}
\tableofcontents
\newpage
\section[Introduction]{Modelling M/EEG data with Bayesian generalised
additive multilevel models}

@@

Here are some useful references to be discussed
(\citeproc{ref-combrisson_exceeding_2015}{Combrisson \& Jerbi, 2015};
\citeproc{ref-ehinger_unfold_2019}{Ehinger \& Dimigen, 2019};
\citeproc{ref-frossard2021}{Frossard \& Renaud, 2021},
\citeproc{ref-frossard2022}{2022}; \citeproc{ref-gramfort2013}{Gramfort,
2013}; \citeproc{ref-hayasaka_validating_2003}{Hayasaka, 2003};
\citeproc{ref-luck_how_2017}{Luck \& Gaspelin, 2017};
\citeproc{ref-maris2007}{Maris \& Oostenveld, 2007};
\citeproc{ref-pedersen_hierarchical_2019}{E. J. Pedersen et al., 2019};
\citeproc{ref-pernet2015}{C. R. Pernet et al., 2015})\ldots{} See also
(\citeproc{ref-maris2011}{Maris, 2011})\ldots{} and
(\citeproc{ref-rosenblatt2018}{Rosenblatt et al., 2018}) (history of
cluster-based approaches and using a data split?)\ldots{} Cluster
failure (\citeproc{ref-eklund2016}{Eklund et al., 2016})\ldots{}

\subsection{Previous modelling work}\label{previous-modelling-work}

Recent example of GLM for EEG (\citeproc{ref-fischer2013}{Fischer \&
Ullsperger, 2013}; \citeproc{ref-wuxfcllhorst2025}{Wüllhorst et al.,
2025})\ldots{} ``Similar approaches have been successfully applied to
EEG time- (Rousselet et al., 2008) and frequency-domain (Cohen and
Cavanagh, 2011) data and allow the simultaneous investigation of
multiple independent variables while preserving the high temporal
resolution of the EEG.''\ldots{} See also (\citeproc{ref-hauk2006}{Hauk
et al., 2006}; \citeproc{ref-rousselet2008}{Rousselet et al.,
2008})\ldots{} Example of two-stage regression analysis (i.e.,
individual-level then group-level, \citeproc{ref-dunagan2024}{Dunagan et
al., 2024})\ldots{}

From Dimigen \& Ehinger (\citeproc{ref-dimigen2021}{2021}): ``Recently,
spline regression has been applied to ERPs (Hendrix, Baayen, \& Bolger,
2017; Kryuchkova,Tucker, Wurm, \& Baayen,2012; Tremblay \& Baayen, 2010;
Tremblay \& Newman, 2015)''\ldots{} GAMMs for EEG data
(\citeproc{ref-abugaber2023}{Abugaber et al., 2023};
\citeproc{ref-meulman2015}{Meulman et al., 2015})\ldots{}

Disentangling overlapping processes
(\citeproc{ref-skukies_brain_2024}{Skukies et al., 2024};
\citeproc{ref-skukies_modelling_2021}{Skukies \& Ehinger, 2021})\ldots{}
Weighting single trials (\citeproc{ref-pernet2022}{C. Pernet,
2022})\ldots{} The LIMO toolbox
(https://onlinelibrary.wiley.com/doi/10.1155/2011/831409)\ldots{} Using
Bayes factors (\citeproc{ref-teichmann2022}{Teichmann, 2022})\ldots{}

@@

See for instance these tutorials
(\citeproc{ref-suxf3skuthy2017}{Sóskuthy, 2017};
\citeproc{ref-winter2016}{Winter \& Wieling, 2016}) or application to
phonetic data (\citeproc{ref-wieling2018}{Wieling, 2018}) or this
introduction (\citeproc{ref-baayen2020}{Baayen \& Linke, 2020}) or these
reference books (\citeproc{ref-hastie2017}{Hastie \& Tibshirani, 2017};
\citeproc{ref-wood2017}{Wood, 2017})\ldots{}

@@

\[
\begin{aligned} 
y_{i} &\sim \mathrm{EF}\left(\mu_{i}, \phi\right)\\
g\left(\mu_i\right) &= A_{i} + \mathbf{X}_{i} \gamma + \sum_{j=1}^{J} f_{j}\left(x_{ij}\right)
\end{aligned}
\]

@@

where \(\beta_{jk}\) is the weight (coefficient) associated with the
\(k\)th basis function \(b_{jk}()\) evaluated at the covariate value
\(x_{ij}\) for the \(j\)th smooth function \(f_{j}\). Splines'
coefficients are penalised\ldots{}

@@

\caption{\label{fig-eeg}Some ERPs in two conditions with 50 trials each,
for a group of 20 participants.}

@@

We then fitted a Bayesian GAM using the \texttt{brms} package
(\citeproc{ref-brms2017}{Bürkner, 2017}, \citeproc{ref-brms2018}{2018};
\citeproc{ref-nalborczyk2019}{Nalborczyk et al., 2019}). We used the
default priors in \texttt{brms}, that is, weakly informative priors. We
ran eight Markov Chain Monte-Carlo (MCMC) to approximate the posterior
distribution, including each 5000 iterations and a warmup of 2000
iterations, yielding a total of \(8 \times (5000-2000) = 24000\)
posterior samples to use for inference. Posterior convergence was
assessed examining trace plots as well as the Gelman--Rubin statistic
\(\hat{R}\).

@@

We then compute the posterior probability of the slope for
\texttt{condition} being above \(0+\epsilon\)
(Figure~\ref{fig-post-prob-test}), with \(\epsilon\) defined as 10\% of
the standard deviation of the raw EEG signal.

@@

\includegraphics[width=1\textwidth,height=\textheight]{brms_meeg_files/figure-pdf/fig-post-prob-ratio-1.pdf}

@@

We compared the ability of the GAMM to correctly estimate the onset and
offset of the ERP difference to widely used methods. First, we conducted
mass-univariate t-tests (thus treating each timestep independently) and
identified the onset and offset of the ERP difference as the first and
last values crossing an arbitrary significance threshold
(\(\alpha = 0.01\)). We then followed the same approach but after
applying different forms of multiplicity correction the the p-values. We
compared two methods that control the false discovery rate (FDR) (i.e.,
BH95, \citeproc{ref-benjamini1995}{Benjamini \& Hochberg, 1995}; and
BY01, \citeproc{ref-benjamini2001}{Benjamini \& Yekutieli, 2001}), one
method that controls the familywise error rate (FWER) (i.e.,
Holm--Bonferroni method, https://www.jstor.org/stable/4615733), and two
cluster-based methods (permutation with a single threshold and TFCE,
\citeproc{ref-smith2009}{Smith \& Nichols, 2009}). The BH95, BY01, and
Holm corrections were applied to the p-values using the
\texttt{p.adjust()} function in \texttt{R}. The cluster-based inference
was implemented using a cluster-sum statistic of squared t-values, as
implemented in \texttt{MNE-Python}
(\citeproc{ref-gramfort2013}{Gramfort, 2013}), called via the \texttt{R}
package \texttt{reticulate} v 1.35.0 (\citeproc{ref-reticulate}{Ushey et
al., 2024}). We also compared these estimates to the onset and offset as
estimated using the binary segmentation algorithm, as implemented in the
\texttt{R} package \texttt{changepoint} v 2.2.4
(\citeproc{ref-changepoint}{Killick et al., 2022a}), and applied
directly to the squared t-values (as in
\citeproc{ref-rousselet_using_2025}{Rousselet, 2025}). For visualisation
and interpretability purposes, we converted p-values to s-values, which
can be interpreted as bits of surprising information, assuming a null
effect (\citeproc{ref-greenland2019}{Greenland, 2019})
(Figure~\ref{fig-corrections}).

@@

Onset/offset estimation methods were assessed using these summary
statistics of the Monte Carlo sampling distributions of onsets: median
absolute error (MAE) and variance, with 10.000 iterations (i.e., 10.000
simulated datasets)\ldots{}

@@

\begin{itemize}
\tightlist
\item
  Create many (e.g., 10 or 20) half train/test splits of the data
\item
  For each fold, estimate the onset/offset on both splits using all
  methods
\item
  Then summarise the distribution of between-split difference across
  folds
\end{itemize}

This will allow checking that the proposed approach produces more
reliable onset/offset estimates.

@@

@@

@@

@@

@@

\bibitem[\citeproctext]{ref-pernet2022}
Pernet, C. (2022). Electroencephalography robust statistical linear
modelling using a single weight per trial. \emph{Aperture Neuro},
\emph{2}, 1--22.
\url{https://doi.org/10.52294/apertureneuro.2022.2.seoo9435}

@@

@@

\bibitem[\citeproctext]{ref-wood2017}
Wood, S. N. (2017). \emph{Generalized Additive Models}. Chapman;
Hall/CRC. \url{https://doi.org/10.1201/9781315370279}

@@

\section{\texorpdfstring{Using the \texttt{R} package and integration
with
\texttt{MNE-Python}}{Using the R package and integration with MNE-Python}}\label{using-the-r-package-and-integration-with-mne-python}

Explain how to use the \texttt{R} package and to integrate it with
\texttt{MNE} epochs\ldots{}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# to{-}do adding some code here...}
\end{Highlighting}
\end{Shaded}

>>>>

\title{Precise temporal localisation of M/EEG effects with Bayesian
generalised additive multilevel models}

\shorttitle{Bayesian modelling of M/EEG data}

@@

\abstract{Time-resolved electrophysiological measurements such as those
offered by magneto- or electro-encephalography (M/EEG) provide a unique
window onto neural activity underlying cognitive processes. Typically,
researchers are interested in testing whether and when such measures
differ across conditions and/or groups. The conventional approach
consists in conducting mass-univariate statistics through time followed
by some form of multiplicity correction (e.g., FDR, FWER) or
cluster-based inference. However, these cluster-based methods have an
important downside: they shift the focus of inference from the timepoint
to the cluster level, thus preventing any conclusion to be made about
the onset or offset of effects (e.g., differences across conditions or
groups). Here, we introduce a \emph{model-based} approch for analysing
M/EEG timeseries such as ERPs or timecourses of decoding performance and
their differences across conditions or groups. This approach relies on
Bayesian generalised additive multilevel models, which output the
posterior probabilility of the effect being above 0 (or above chance) at
every timestep, while naturally taking into account the temporal
dependencies and between-subject variability present in such data. Using
both simulation and actual EEG data, we show that the proposed approach
largely outperforms conventional methods in determining both the onset
and offset of M/EEG effects (e.g., ERPs difference, decoding
performance), producting more precise and more reliable estimates. We
provide an R package implementing the approach and illustrate how to
integrate it into M/EEG statistical pipelines in MNE-Python.}

@@

\hypertarget{toc}{}
\tableofcontents
\newpage
\section[Introduction]{Precise temporal localisation of M/EEG effects
with Bayesian generalised additive multilevel models}

@@

Here are some useful references to be discussed
(\citeproc{ref-combrisson_exceeding_2015}{Combrisson \& Jerbi, 2015};
\citeproc{ref-ehinger_unfold_2019}{Ehinger \& Dimigen, 2019};
\citeproc{ref-frossard2021}{Frossard \& Renaud, 2021},
\citeproc{ref-frossard2022}{2022}; \citeproc{ref-gramfort2013}{Gramfort,
2013}; \citeproc{ref-hayasaka_validating_2003}{Hayasaka, 2003};
\citeproc{ref-luck_how_2017}{Luck \& Gaspelin, 2017};
\citeproc{ref-maris2007}{Maris \& Oostenveld, 2007};
\citeproc{ref-pedersen_hierarchical_2019}{E. J. Pedersen et al., 2019};
\citeproc{ref-pernet2015}{Pernet et al., 2015})\ldots{} See also Maris
(\citeproc{ref-maris2011}{2011}) and Rosenblatt et al.
(\citeproc{ref-rosenblatt2018}{2018}) (history of cluster-based
approaches)\ldots{} Clusters failures (\citeproc{ref-eklund2016}{Eklund
et al., 2016})\ldots{}

\subsection{Previous work}\label{previous-work}

Recent example of GLM for EEG (\citeproc{ref-fischer2013}{Fischer \&
Ullsperger, 2013}; \citeproc{ref-wuxfcllhorst2025}{Wüllhorst et al.,
2025})\ldots{} See also (\citeproc{ref-hauk2006}{Hauk et al., 2006};
\citeproc{ref-rousselet2008}{Rousselet et al., 2008})\ldots{} Example of
two-stage regression analysis (i.e., individual-level then group-level,
\citeproc{ref-dunagan2024}{Dunagan et al., 2024})\ldots{}

From Dimigen \& Ehinger (\citeproc{ref-dimigen2021}{2021}): Recently,
spline regression has been applied to ERPs (e.g.,
\citeproc{ref-hendrix2017}{Hendrix et al., 2017};
\citeproc{ref-kryuchkova2012}{Kryuchkova et al., 2012})\ldots{} GAMMs
for EEG data (\citeproc{ref-abugaber2023}{Abugaber et al., 2023};
\citeproc{ref-meulman2015}{Meulman et al., 2015})\ldots{}

Disentangling overlapping processes
(\citeproc{ref-skukies_brain_2024}{Skukies et al., 2024};
\citeproc{ref-skukies_modelling_2021}{Skukies \& Ehinger, 2021})\ldots{}
Weighting single trials (\citeproc{ref-pernet2022}{Pernet,
2022})\ldots{} The LIMO toolbox (\citeproc{ref-pernet2011}{Pernet et
al., 2011})\ldots{}

Using Bayes factors for decoding performance
(\citeproc{ref-teichmann2022}{Teichmann, 2022})\ldots{}

\subsection{Bayesian regression
modelling}\label{bayesian-regression-modelling}

Short intro/recap about Bayesian (linear and generalised) regression
models\ldots{}

@@

See for instance these tutorials
(\citeproc{ref-suxf3skuthy2017}{Sóskuthy, 2017};
\citeproc{ref-winter2016}{Winter \& Wieling, 2016}) or application to
phonetic data (\citeproc{ref-wieling2018}{Wieling, 2018}) or this
introduction (\citeproc{ref-baayen2020}{Baayen \& Linke, 2020}) or these
reference books (\citeproc{ref-hastie2017}{Hastie \& Tibshirani, 2017};
\citeproc{ref-wood2017}{Wood, 2017a})\ldots{} application to
pupillometry (\citeproc{ref-vanrij2019}{Rij et al., 2019})\ldots{}
GAMLSS for neuroimaging data (\citeproc{ref-dinga2021}{Dinga et al.,
2021})\ldots{}

@@

\[
\begin{aligned} 
y_{i} &\sim \mathrm{EF}\left(\mu_{i}, \phi\right)\\
g\left(\mu_i\right) &=  \underbrace{A_{i} + \mathbf{X}_{i} \gamma}_{\text{parametric part}} + \underbrace{\sum_{j=1}^{J} f_{j}\left(x_{ij}\right)}_{\text{non-parametric part}}
\end{aligned}
\]

@@

where \(\beta_{jk}\) is the weight (coefficient) associated with the
\(k\)th basis function \(b_{jk}()\) evaluated at the covariate value
\(x_{ij}\) for the \(j\)th smooth function \(f_{j}\). Splines
coefficients are penalised (usually through the squared of the smooth
functions' second derivative) in a way that can be interpreted as a
prior on the ``wiggliness'' of the function\ldots{}

\subsection{Bayesian generalised additive multilevel
models}\label{bayesian-generalised-additive-multilevel-models}

Now describe the Bayesian GAMM\ldots{} Proper inclusion of
varying/random effects in the model specification protects against
overly wiggly curves (\citeproc{ref-baayen2020}{Baayen \& Linke,
2020})\ldots{}

@@

\caption{\label{fig-eeg}Averaged (mean) simulated EEG activity in two
conditions with 50 trials each, for a group of 20 participants. The
error band represents the mean plus/minus 1 standard error of the mean.}

@@

We then fitted a Bayesian GAM using the \texttt{brms} package
(\citeproc{ref-brms2017}{Bürkner, 2017}, \citeproc{ref-brms2018}{2018};
\citeproc{ref-nalborczyk2019}{Nalborczyk et al., 2019}). We used the
default priors in \texttt{brms}, that is, weakly informative priors. We
ran eight Markov Chain Monte-Carlo (MCMC) to approximate the posterior
distribution, including each 5000 iterations and a warmup of 2000
iterations, yielding a total of \(8 \times (5000-2000) = 24000\)
posterior samples to use for inference. Posterior convergence was
assessed examining trace plots as well as the Gelman--Rubin statistic
\(\hat{R}\). The \texttt{brms} package uses the same syntax as the
\texttt{R} package \texttt{mgcv} v 1.9-1 (\citeproc{ref-mgcv}{Wood,
2017b}) for specifying smooth effects.

@@

We then compute the posterior probability of the slope for
\texttt{condition} being above \(0+\epsilon\)
(Figure~\ref{fig-post-prob-test}), with \(\epsilon := 0.05\), which can
be interpreted as the smallest effect size of interest.

@@

\includegraphics[width=0.75\textwidth,height=\textheight]{brms_meeg_files/figure-pdf/fig-post-prob-ratio-1.pdf}

@@

We compared the ability of the GAMM to correctly estimate the onset and
offset of the ERP difference to widely used methods. First, we conducted
mass-univariate t-tests (thus treating each timestep independently) and
identified the onset and offset of the ERP difference as the first and
last values crossing an arbitrary significance threshold
(\(\alpha = 0.01\)). We then followed the same approach but after
applying different forms of multiplicity correction the the p-values. We
compared two methods that control the false discovery rate (FDR) (i.e.,
BH95, \citeproc{ref-benjamini1995}{Benjamini \& Hochberg, 1995}; and
BY01, \citeproc{ref-benjamini2001}{Benjamini \& Yekutieli, 2001}), one
method that controls the familywise error rate (FWER) (i.e.,
Holm--Bonferroni method, \citeproc{ref-holm1979}{Holm, 1979}), and two
cluster-based methods (permutation with a single threshold and TFCE,
\citeproc{ref-smith2009}{Smith \& Nichols, 2009}). The BH95, BY01, and
Holm corrections were applied to the p-values using the
\texttt{p.adjust()} function in \texttt{R}. The cluster-based inference
was implemented using a cluster-sum statistic of squared t-values, as
implemented in \texttt{MNE-Python}
(\citeproc{ref-gramfort2013}{Gramfort, 2013}), called via the \texttt{R}
package \texttt{reticulate} v 1.35.0 (\citeproc{ref-reticulate}{Ushey et
al., 2024}). We also compared these estimates to the onset and offset as
estimated using the binary segmentation algorithm, as implemented in the
\texttt{R} package \texttt{changepoint} v 2.2.4
(\citeproc{ref-changepoint}{Killick et al., 2022a}), and applied
directly to the squared t-values (as in
\citeproc{ref-rousselet_using_2025}{Rousselet, 2025}). For visualisation
and interpretability purposes, we converted p-values to s-values, which
can be interpreted as bits of surprising information, assuming a null
effect (\citeproc{ref-greenland2019}{Greenland, 2019})
(Figure~\ref{fig-corrections}).

@@

Onset/offset estimation methods were assessed using the median absolute
error (MAE) and variance of 10.000 simulated datasets\ldots{}

@@

\begin{itemize}
\tightlist
\item
  Create many (e.g., 10 or 20) half train/test splits of the data
\item
  For each fold, estimate the onset/offset on both splits using all
  methods
\item
  Then summarise the distribution of onset/offset with the median and
  variance across folds
\end{itemize}

This will allow checking that the proposed approach produces reliable
onset/offset estimates.

@@

We kept the exemplary models simple, but can be extended by adding
varying/random effects (intercept and slope) for item (e.g.,
word)\ldots{} but also continuous predictors at the trial level?

@@

\bibitem[\citeproctext]{ref-dinga2021}
Dinga, R., Fraza, C. J., Bayer, J. M. M., Kia, S. M., Beckmann, C. F.,
\& Marquand, A. F. (2021). \emph{Normative modeling of neuroimaging data
using generalized additive models of location scale and shape}.
\url{http://dx.doi.org/10.1101/2021.06.14.448106}

@@

\bibitem[\citeproctext]{ref-hendrix2017}
Hendrix, P., Bolger, P., \& Baayen, H. (2017). Distinct ERP signatures
of word frequency, phrase frequency, and prototypicality in speech
production. \emph{Journal of Experimental Psychology: Learning, Memory,
and Cognition}, \emph{43}(1), 128--149.
\url{https://doi.org/10.1037/a0040332}

\bibitem[\citeproctext]{ref-holm1979}
Holm, S. (1979). A simple sequentially rejective multiple test
procedure. \emph{Scandinavian Journal of Statistics}, \emph{6}(2),
65--70. \url{http://www.jstor.org/stable/4615733}

@@

\bibitem[\citeproctext]{ref-kryuchkova2012}
Kryuchkova, T., Tucker, B. V., Wurm, L. H., \& Baayen, R. H. (2012).
Danger and usefulness are detected early in auditory lexical processing:
Evidence from electroencephalography. \emph{Brain and Language},
\emph{122}(2), 81--91. \url{https://doi.org/10.1016/j.bandl.2012.05.005}

@@

\bibitem[\citeproctext]{ref-pernet2022}
Pernet, C. R. (2022). Electroencephalography robust statistical linear
modelling using a single weight per trial. \emph{Aperture Neuro},
\emph{2}, 1--22.
\url{https://doi.org/10.52294/apertureneuro.2022.2.seoo9435}

\bibitem[\citeproctext]{ref-pernet2011}
Pernet, C. R., Chauveau, N., Gaspar, C., \& Rousselet, G. A. (2011).
LIMO EEG: A Toolbox for Hierarchical LInear MOdeling of
ElectroEncephaloGraphic Data. \emph{Computational Intelligence and
Neuroscience}, \emph{2011}, 1--11.
\url{https://doi.org/10.1155/2011/831409}

@@

\bibitem[\citeproctext]{ref-vanrij2019}
Rij, J. van, Hendriks, P., Rijn, H. van, Baayen, R. H., \& Wood, S. N.
(2019). Analyzing the Time Course of Pupillometric Data. \emph{Trends in
Hearing}, \emph{23}. \url{https://doi.org/10.1177/2331216519832483}

@@

\bibitem[\citeproctext]{ref-wood2017}
Wood, S. N. (2017a). \emph{Generalized Additive Models}. Chapman;
Hall/CRC. \url{https://doi.org/10.1201/9781315370279}

\bibitem[\citeproctext]{ref-mgcv}
Wood, S. N. (2017b). \emph{Generalized additive models: An introduction
with r} (2nd ed.). Chapman; Hall/CRC.

@@

\section{\texorpdfstring{Integration with
\texttt{MNE-Python}}{Integration with MNE-Python}}\label{integration-with-mne-python}

Explain how to use the \texttt{R} package with \texttt{MNE}
epochs\ldots{}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# suggest a package name}
\FunctionTok{library}\NormalTok{(available)}
\FunctionTok{suggest}\NormalTok{(}
    \AttributeTok{text =} \StringTok{"Time{-}resolved electrophysiological measurements such as those offered by magneto{-} or electro{-}encephalography (M/EEG) provide a unique window onto neural activity underlying cognitive processes. Typically, researchers are interested in testing whether and when such measures differ across conditions and/or groups. The conventional approach consists in conducting mass{-}univariate statistics through time followed by some form of multiplicity correction (e.g., FDR, FWER) or cluster{-}based inference. However, these cluster{-}based methods have an important downside: they shift the focus of inference from the timepoint to the cluster level, thus preventing any conclusion to be made about the onset or offset of effects (e.g., differences across conditions or groups). Here, we introduce a *model{-}based* approch for analysing M/EEG timeseries such as ERPs or timecourses of decoding performance and their differences across conditions or groups. This approach relies on Bayesian generalised additive multilevel models, which output the posterior probabilility of the effect being above 0 (or above chance) at every timestep, while naturally taking into account the temporal dependencies and between{-}subject variability present in such data. Using both simulation and actual EEG data, we show that the proposed approach largely outperforms conventional methods in determining both the onset and offset of M/EEG effects (e.g., ERPs difference, decoding performance), producting more precise and more reliable estimates. We provide an R package implementing the approach and illustrate how to integrate it into M/EEG statistical pipelines in MNE{-}Python."}
\NormalTok{    )}

\NormalTok{available}\SpecialCharTok{:::}\FunctionTok{namr}\NormalTok{(}
    \AttributeTok{title =} \StringTok{"Precise temporal localisation of M/EEG effects with Bayesian generalised additive multilevel models"}\NormalTok{,}
    \AttributeTok{verb =} \ConstantTok{TRUE}
\NormalTok{    )}

\CommentTok{\# to{-}do adding some code here...}
\end{Highlighting}
\end{Shaded}
